---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                      |
|                                                   | 1.  124255 - Challengers - Natasha Wairimu Gichira                                                                                |
|                                                   |                                                                                                      |
|                                                   | 2.  124562 - Challengers -  Gitonga Ryan Munene                                                                                |
|                                                   |                                                                                                      |
|                                                   | 3.  120415 - Challengers - Emmanuel Agre                                                                                |
|                                                   |                                                                                                      |
|                                                   | 4.  118211 - Challengers - Fredrick Koech                                                                                |
|                                                   |                                                                                                      |
|                                                   | 5.  124422 - Challengers -  Dennis Muriuki                                                                                |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Challengers                                                                                                      |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                              |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                             |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                          |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                           |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# \<Loading a dataset>

Describe the code chunk here:
Here the dataset is being loaded from the root folder
```{r Your Second Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
# STEP 3. Load the Dataset ----
student_performance_dataset <-
  read_csv("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset copy.CSV",)
```

Describe the next code chunk here:
Here the knitR function is installed with its dependencies
```{r Your Third Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```## knitr - for dynamic report generation ----
if (!is.element("knitr", installed.packages()[, 1])) {
  install.packages("knitr", dependencies = TRUE)


```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

# \<You can Provide Another Appropriate Title Here\>

Describe the code chunk here:

```{r Your Fifth Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
```

**etc.** as per the lab submission requirements.
